Interpolation and extrapolation-based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel

### 2023-01-17 Article.tex
Update Whole article for corrections

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\AARE}{\text{E}_\text{AAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

% This is used to add comments into the text
%
% Will have to be removed from final version
%
\usepackage{soul}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150}
\DeclareRobustCommand{\OP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
\DeclareRobustCommand{\OPP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}

@@

\title{Interpolation and extrapolation based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, 65016, France}
\address[ETS]{École de Technologie Supérieure, 1100 Rue Notre Dame O, Montréal, QC H3C 1K3, Canada}

\begin{abstract}
\textcolor{red}{In the present work, a critical analysis of the most commonly used analytical models as well as recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them}. To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Geleeble $3800$ thermomechanical simulator. The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius, and the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output. The Mean Absolute Relative Error (MARE) and the Root Mean Square Error (RMSE) values were used to quantify the predictive accuracy of the analyzed models. The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented significant error, MARRE of  $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with about $3.56\%$ error. The Artificial Neural Network model, on the other hand, showed excellent agreement, less than $0.62\%$ error, between the predicted and experimental flow curves. To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested. The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability with a notable superiority for the Arrhenius model compared to the other two. The Artificial Neural Networks model was however, still the most performant compared to all the models. A correlation factor is proposed to extend the applicability of some of the investigated models to deformation conditions not included in the original experimental plan.
\end{abstract}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Large size forged blocks made of medium carbon high-strength steels are extensively used in automotive industry as dies for the production of bumpers and dashboards through the plastic injection process. The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and quench $\&$ temper heat treatment process to achieve the desired mechanical properties  \cite{chadha2017deformation,chadha2018influence,murugesan2019two}. In recent years, in order to respond to the market demand, larger size forgings need to be produced. In parallel, more stringent condition on chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block are required. Among the three manufacturing steps (casting, forging, heat treatment), forging is the one where the most important microstructural changes take place and influences the final properties that could be achieved \cite{murugesan2019hybrid,chadha2020microstructure,sripada2022effect}. Open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, concomitantly take place with softening phenomena such as   recovery and recrystallization under static and/or dynamic \cite{tian2022deformation,tavakoli2019ferrite}. It has also been reported that phase transformation could take place during deformation. The extent and intensity of the above strengthening or softening phenomena strongly depend on three macroscopic quantities \ie the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$  \cite{ ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}.

Considering the large size of the blocks, a purely experimental approach, based on trial and error, could not be used by industry and reliable predictive tools, such a Finite Element analysis (FEA) codes have been developed and are commercially available. However, the prediction reliability of such analyses is dependent on the accuracy of the material constitutive model, which describes the mutual interactions between strain, strain rate, and temperature during deformation. Precipitation and phase changes as mentioned above are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides. Hence most of the constitutive models depend on macroscopic parameters that influence the hardening and softening of the material. A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed among them, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes. Despite their simplicity, each of them suffer from shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from lack of non-coupling between strain, strain rate and temperature  while the HS model is better adapted for higher strain rate deformation conditions \cite{chadha2018approach}. To circumvent these shortcomings, several modified forms of models have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}. However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, could not be accurately predicted and none of the models is able to accurately predict flow behavior outside the experimental testing interval that was used to determine the model constants. Due to its more physics-based formulation, the ZA model and its modified form, MZA, \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021} and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS  models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}. The Arrhenius formulation has been revised several times for a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}. To overcome the strong dependency of the models to a specific alloy, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type. This formulation is based on the MZA model and polynomial functions of undefined order that are used during the identification. However, in the PTM model, the high order of the polynomial function (up to $10$ in some cases) can affect its accuracy.

Artificial Neural Network (ANN) is an approach to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law. It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model. Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited. Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships. Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB}. Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software as reported by Pantalé \eal \cite{Pantale-2021}. In fact, the implementation of constitutive model in a FEA code requires the derivatives of this model with respect to strain, strain rate and temperature.

Although progress has been made in improvement of constitutive models to better predict the flow stress behavior of materials, there is still a problem with the efficiency of all the above models. Indeed, a model is considered appropriate to the prediction of the material's behavior when its predictions and experimental results correlate well. It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those it was identified for. In other words, can interpolation and extrapolation techniques be used to extent the applicability of a constitutive equation for different materials and processing windows?

The present work aims to address the above question using a combination of the recently introduced PTM model and ANN. To this end, initially, hot compression tests, simulating the open die forging process, were carried out and the generated flow curves were modeled using the above mentioned constitutive equations and an ANN model developed in this work. Then the interpolation and extrapolation capabilities of each model is evaluated and a solution is proposed that responds to the main question of the paper. The results are validated based on experimental work carried out in the present work and data obtained from the literature.

@@

The material used in this study is a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[h!]
\centering
\caption{Chemical composition of medium carbon steel, Fe = balance.}
\begin{tabular}{lccccccc}
	\hline
	Element &  C   &  Mn  &  Mo  &  Si  &  Ni  &  Cr  &  Cu  \\ \hline
	Wt~\%   & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17 \\ \hline
\end{tabular}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the 5 temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the 6 strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as a lubricating material at the contact surface of the anvils and samples to minimize friction during testing. As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients. They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation. During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine. After compression, the specimen is quickly quenched to freeze its microstructure for later analysis. Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process.}
\label{fig:GleebleProcess}
\end{figure}

The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as true stress and true strain according to L-gauge where the formula to get those curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2r_0$ and $F$ is the force as measured by Gleeble load cell. As there are noises from raw data, savgolfilter method from scipy library is used to remove noise and have more smooth data. For further usage of data in numerical simulation elastic parts have been removed.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/rawData}
\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
\label{fig:RawData}
\end{figure}
All data curve contains $700$ equidistant strain values up-to $\varepsilon=0.7$.
So, there are $6$ strain rates and $5$ temperatures, the database consists of $21~000$ data points.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{buckley2001deformation}. The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time and thus friction increases. The increase of stresses observed at the beginning of the deformation up to $0.1$ is due to the work hardening (WH). After $0.1$ up to $0.2$ the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of work-hardening rate. This behavior describes that thermal softening becomes more and more predominant until it exceeds WH. At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening. This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$ except those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and strain rate of $0.1$ $\text{s}^{-1}$ ; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$). Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates. In contrast, at higher strain rates and lower temperatures, the higher work hardening rate slows down the rate of softening due to DRX, and therefore, both the peak stress and the onset of steady-state flow are shifted to higher strain levels. In fact, the drop observed in
stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$. As an example, Figure \ref{fig:Micrography} shows the microstructures of medium carbon held during $5$~min at $1260\celsius$ before and after the compression phase.
\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/BeforeCompM}
\caption{Before hot compression}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/AfterCompM}
\caption{After hot compression}
\end{subfigure}
\caption{Optical micrographs of a medium carbon steel before (a) and after (b) hot compression.}
\label{fig:Micrography}
\end{figure}
As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the 6 proposed flow laws will be presented in the next section in order to predict the behavior of the material in any test condition.

%----------------------------------------------------------------------------------
\section{Identification of constitutive flow laws parameters\label{sec:ConstLaws}}
%----------------------------------------------------------------------------------
%----------------------------------------------------------------------------------
\subsection{The Johnson-Cook model\label{sec:JC}}
%----------------------------------------------------------------------------------

>>>>

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

% This is used to add comments into the text
%
% Will have to be removed from final version
%
\usepackage{soul}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150}
\sethlcolor{VWyellow}

\DeclareRobustCommand{\OP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
\DeclareRobustCommand{\OPP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
\DeclareRobustCommand{\CR}[1]{\textcolor{red}{#1}}
\DeclareRobustCommand{\SP}[1]{\textcolor{red}{\sout{#1}}}

@@

\title{Interpolation and extrapolation-based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, 65016, France}
\address[ETS]{École de technologie supérieure, 1100 Notre Dame St. W., Montreal, QC H3C 1K3, Canada}

\begin{abstract}
In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius \CR{models}, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
The Mean Absolute Relative Error \CR{($\MARE$)} and the Root Mean Square Error \CR{($\RMSE$)} values were used to quantify the predictive accuracy of the analyzed models.
The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented \CR{a} significant error, \CR{$\MARE$} of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability\CR{,} with the notable superiority of the Arrhenius model over the other two.
The Artificial Neural Networks model was\CR{,} however, still the most performant among all the models.
\SP{A correlation factor was proposed to extend the applicability of some of the investigated models to deformation conditions not included in the original experimental plan.}\OP{Has to be removed}
\end{abstract}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Large size forged blocks made of medium carbon high-strength steels are extensively used in the automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and a quench and temper heat treatment process to achieve the desired mechanical properties \cite{chadha2017deformation, chadha2018influence, murugesan2019two}.
In recent years, in order to respond to the market demand, larger size forgings have had to be produced.
In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block have been required.
Of the three manufacturing steps (casting, forging and heat treatment), forging is where the most important microstructural changes take place, and which greatly influences the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic \CR{thermomechanical loads} \cite{tian2022deformation, tavakoli2019ferrite}.
It has also been reported that phase transformation can occur during deformation.
The extent and intensity of the above phenomena strongly depend on three macroscopic quantities\CR{,} namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, Ashtiani-2012, He-2013, Changizian-2012}.

Considering the large size of blocks, a purely experimental approach, based on trial and error, can not be used by industry, and therefore, reliable predictive tools, such a Finite Element analysis (FEA) codes, have been developed, and are commercially available.
However, the prediction reliability of such analyses is a function of the accuracy of the material constitutive model, which describes the mutual interactions between the strain, the strain rate, and the temperature during deformation.
As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
Hence, most constitutive models depend on macroscopic parameters which influence the hardening and softening of the material.
A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed.
Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate \SP{deformation} conditions \cite{chadha2018approach}.
To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, \CR{cannot} be accurately predicted\CR{,} and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
Due to its more physics-based formulation, the ZA model and its modified form, MZA\SP{,} \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
The Arrhenius formulation has been revised \CR{repeatedly} to achieve a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
This formulation is based on the MZA model and the polynomial functions of undefined order that are used during the identification.
However, in the PTM model, the high order of the polynomial function (up-to $10$ in some cases) can affect its accuracy.

The Artificial Neural Network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to strain, strain rate and temperature.

Although progress has been made in improving constitutive models to better predict the flow stress behavior of materials, problem still persist with the \CR{models'} efficiency.
Indeed, a model is considered appropriate for predicting the material's behavior if its predictions and experimental results correlate well.
It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those for which it was identified.
In other words, the question is whether interpolation and extrapolation techniques can be used to extend the applicability of a constitutive equation for different \SP{materials and}\OP{Out of this scope concerning different materials} processing windows.

The present work aims to address the preceding question using \SP{a combination of} the recently introduced \SP{PTM model and} ANN \CR{model}.\OP{Objective updated}
To this end, initially, hot compression tests, simulating the open die forging process, are carried out and the flow curves generated are modeled using the above--mentioned constitutive equations and an ANN model developed in this work.
Then, the interpolation and extrapolation capabilities of each model are evaluated \SP{and a solution proposed, responding to the main question of the paper}.
The results are validated based on experimental work carried out \CR{herein} and on data obtained from the literature.

@@

The material used in this study consists of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[h!]
\centering
\caption{Chemical composition of medium carbon steel, Fe = balance}
\begin{tabular}{lccccccc}
	\hline
	Element &  C   &  Mn  &  Mo  &  Si  &  Ni  &  Cr  &  Cu  \\ \hline
	Wt~\%   & 0.30 & 0.89 & 0.52 & 0.34 & 0.68 & 1.86 & 0.17 \\ \hline
\end{tabular}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$\CR{,} with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process}
\label{fig:GleebleProcess}
\end{figure}

The stress-strain curves are automatically exported from the Gleeble thermomechanical simulator system as the true stress and true strain according to the L-gauge, where the formula to get the curves is given by $\sigma=F/A$ and $\varepsilon=\ln\left(h_0+\Delta h / h_0\right)$ or C-gauge, having the following formulas: $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln\left(d/(d+\Delta d)\right)$ with $d = 2r_0$, and where $F$ is the force as measured by the Gleeble load cell.
As raw data contains noises, \CR{the} savgol\_filter method from the scipy library is used to remove noise and provide smoother data.
To allow further use of the data in numerical simulations, elastic parts are removed.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/rawData}
\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$}
\label{fig:RawData}
\end{figure}
All data curves contain $700$ equidistant strain values up-to $\varepsilon=0.7$.
Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of \CR{$21,000$} data points.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$\CR{,} but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, and then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{buckley2001deformation}.
The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time, and friction thus increases.
The increase of stress observed at the beginning of the deformation and up-to $0.1$ is due to work hardening (WH).
After $0.1$ and up-to $0.2$, the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of the work-hardening rate.
This behavior indicates that thermal softening becomes more and more predominant until it exceeds WH.
At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening.
This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$, except for those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and a $0.1$ $\text{s}^{-1}$ strain rate; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates.
In contrast, at higher strain rates and lower temperatures, the higher work hardening rate slows down the rate of softening due to DRX, and therefore, both the peak stress and the onset of steady-state flow are shifted to higher strain levels.
In fact, the drop observed in
stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$.

As an example, Figure \ref{fig:Micrography} shows the medium carbon \CR{microstructures} held for $5$~min at $1260\celsius$ before and after the compression phase.
\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/BeforeCompM}
\caption{Before hot compression}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/AfterCompM}
\caption{After hot compression}
\end{subfigure}
\caption{Optical micrographs of a medium carbon steel (a) before and (b) after hot compression}
\label{fig:Micrography}
\end{figure}
As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get austenitized grain on the one hand, and on the other hand, held for $1$ minute at $1150^\circ$C before compression with a $0.001~\text{s}^{-1}$ strain rate.
\SP{The results reported in Figure \ref{fig:RawData},will be used in the next section to identify the parameters of the $6$ proposed flow laws in order to see which mode will matches with experimental.}
The data presented in Figure \ref{fig:RawData} will be utilized in the following section to determine the parameters of the $6$ flow laws proposed and to determine which model most closely aligns with experimental results.

%----------------------------------------------------------------------------------
\section{Identification of Constitutive Flow Laws Parameters\label{sec:ConstLaws}}
%----------------------------------------------------------------------------------
%----------------------------------------------------------------------------------
\subsection{The Johnson-Cook model\label{sec:JC}}
%----------------------------------------------------------------------------------
